Matched Source Waveform Inversion for Transmitted Waves

### 2024-07-23 repro/papers/awinum/paper.tex
LBFGS and other updates

The gradient (or weighted gradient), together with the value, are the
inputs to first-order methods such as steepest descent and
Limited-Memory Broyden-Fletcher-Goldfarb-Shanno
iterations. Methods more closely related to Newton iteration require
more involved computations (see for instance \cite{Kaufman:75}.

@@

\plot{chwd20}{width=\textwidth}{Data for homogeneous model $m_0$: 20
  sources at $x=3000$ m, 201 receivers at $x=5000$ m.}

>>>>

The gradient (or weighted gradient), together with the value, are the
inputs to first-order methods such as steepest descent and
Limited-Memory Broyden-Fletcher-Goldfarb-Shanno
iterations. Methods more closely related to Newton iteration require
more involved computations (see for instance \cite{Kaufman:75}).

@@

\begin{figure}[H]   
\begin{center}
\includegraphics[width=\textwidth]{project/Fig/chwd20}
\caption{Data from the homogeneous model $m_0$ acquired using 20 sources located along a vertical line at $x=3000$ m and 181 receivers at $x=5000$ m.}
\label{fig:chwd20}
\end{center}
\end{figure}

%\plot{chwd20}{width=\textwidth}{Data for homogeneous model $m_0$: 20
%sources at $x=3000$ m, 201 receivers at $x=5000$ m.}
